The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-10-30 manuscript/manuscript.qmd
Make methods noise description more explicit

For each noise structure, we simulated five different magnitudes of noise ($\Lambda$).
$\Lambda$ was calculated as a multiple ($c$) of the average daily measles incidence ($\langle \Delta I_{M} \rangle$): $\Lambda = c \cdot \langle \Delta I_{M} \rangle \text{where} c \in	\{1, 2, 4, 6, 8 \}$.
For the Poisson-noise scenarios, independent draws from a Poisson distribution with mean $\lambda = \Lambda$ were simulated to produce the noise time series.
For the dynamical noise scenarios, the vaccination rate at birth was set to 85.38%, 73.83%, 50.88%, 27.89%, and 4.92% to produce equivalent mean daily noise values (to within 2 decimal places): $\Lambda = \langle \Delta I_{R} \rangle = c \cdot \langle \Delta I_{M} \rangle$.
100 time series of 100 years were simulated for each scenario, before summarizing the distributions of outbreak detection methods.

>>>>

For each noise structure, we simulated five different magnitudes of noise ($\Lambda$), representing the average daily noise incidence.
$\Lambda$ was calculated as a multiple ($c$) of the average daily measles incidence ($\langle \Delta I_{M} \rangle$): $\Lambda =   c \cdot \langle \Delta I_{M} \rangle \text{where} c \in \{1, 2, 4, 6, 8 \}$.
For the Poisson-noise scenarios, independent draws from a Poisson distribution with mean $c \cdot \langle \Delta I_{M} \rangle$ were simulated to produce the noise time series i.e., $\Lambda = \text{Pois}\left( c \cdot \langle \Delta I_{M} \rangle \right)$.
For the dynamical noise scenarios, the rubella vaccination rate at birth was set to 85.38%, 73.83%, 50.88%, 27.89%, and 4.92% to produce equivalent values of $\Lambda$ (to within 2 decimal places): $\Lambda = \langle \Delta I_{R} \rangle + \text{Pois}\left( 0.15 \cdot \langle \Delta I_{R} \rangle \right)$.
100 time series of 100 years were simulated for each scenario, before summarizing the distributions of outbreak detection methods.
